Irt plot extra

### 2022-02-22 manuscript.Rmd
corrplot significant correlation highlighted

#if you dont have LaTeX installed run the following lines
#install.packages("tinytex")
#tinytex::install_tinytex()
```

@@

                    K[label = 'Long LEBA: 23-item', style = filled, fillcolor = Beige]

@@

                    O[label = 'Short LEBA: 18-item',style = filled, fillcolor = Beige]

@@

correlations <- psych::polychoric(EFA.data, correct = 0)
upper <- correlations$rho[upper.tri(correlations$rho, diag = F)]

@@

corplot <- ggcorrplot(correlations$rho, hc.order = TRUE, outline.col = "white", type = "lower", legend.title = "Correlation",
           ggtheme = ggplot2::theme_minimal(),tl.srt = 90,colors = c("#E64B35FF", "white", "#3C5488FF") )+
  theme( panel.grid.major = element_blank(),
         axis.text.x = element_text(size = 8),
         axis.text.y = element_text(size = 8),
         panel.border = element_rect(color = "black",
                                    fill = NA,
                                    size = 1))
#p.mat <- cor_to_p(correlations$rho, 428, method = "polychoric")
#to show pvalue in the fig add p.mat=p.mat
ggsave("Manuscript.figures/corplot.png",corplot, width = 6, height = 6, dpi = 600, bg ="white")

@@

```{r echo = FALSE, results = 'asis', cache = FALSE}
papaja::render_appendix('appendix-1.Rmd')
```

>>>>

install.packages("correlation")
#if you dont have LaTeX installed run the following lines
#install.packages("tinytex")
#tinytex::install_tinytex()
```

@@

                    K[label = 'LEBA long format: 23-item', style = filled, fillcolor = Beige]

@@

                    O[label = 'LEBA short format: 18-item', style = filled, fillcolor = Beige]

@@

correlations <- psych::polychoric(EFA.data, correct = 0)

upper <- correlations$rho[upper.tri(correlations$rho, diag = F)]

@@

p.mat <- correlation::cor_to_p(correlations$rho, 428, method = "polychoric")

corplot <- ggcorrplot(correlations$rho, p.mat=p.mat$p, insig = "pch", hc.order = FALSE, outline.col = "white", type = "lower", legend.title = "Correlation",sig.level = 0.05, pch.cex=1.8,
                      # insig = "blank",
           ggtheme = ggplot2::theme_minimal(),tl.srt = 90,colors = c("#E64B35FF", "white", "#3C5488FF") )+
  theme( panel.grid.major = element_blank(),
         axis.text.x = element_text(size = 8),
         axis.text.y = element_text(size = 8),
         panel.border = element_rect(color = "black",
                                    fill = NA,
                                    size = 1))
#to show pvalue in the fig add p.mat=p.mat
ggsave("Manuscript.figures/corplot.png",corplot, width = 12, height = 8.5, dpi = 600, bg ="white")

@@
